Total Score

### 2023-02-02 src/MSAtotal_scores.Rmd
calculated total scores using EAL data

climate_risk_data <- read_sheet("https://docs.google.com/spreadsheets/d/1HZCeNGf61RJ9GJs3cLJcl9aNpvmPMBF1Yoss2fytltc/edit#gid=2045475301") %>% 
  select(cbsa, normalized_inverted_climate_risk)

@@

# reorder columns
col_order <-c("cbsa", "city_msa", "state", "real_estate_score", "landlord_score", "normalized_annual_renewable", "normalized_irr", "inverted_n_total_co2", "normalized_inverted_climate_risk", "inverted_n_health_emissions_cost")

@@

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(total_score_owen = cbsa, #this is just a place holder
         real_estate_score = as.numeric(real_estate_score),
         landlord_score = as.numeric(landlord_score)
  )

@@

@@

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(score_climate50_prop = cbsa)#this is just a place holder

size <- dim(criteria_all)
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$normalized_inverted_climate_risk[i]
                  )
  criteria_all$score_climate50_prop[i] = weighted.mean(cbsa_data, weights_climate50_prop) 
}
```

@@

criteria_all <- criteria_all %>% 
  rename(financial_score = normalized_irr,
         climate_impact = inverted_n_total_co2,
         health_impact = inverted_n_health_emissions_cost,
         electricity = normalized_annual_renewable,
         climate_risk = normalized_inverted_climate_risk) %>% 
  mutate_if(is.numeric, ~round(., 5))

sheet_write(criteria_all, ss = "https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=0", sheet = "criteria_all")
```

>>>>

climate_risk_data <- read_sheet("https://docs.google.com/spreadsheets/d/1HZCeNGf61RJ9GJs3cLJcl9aNpvmPMBF1Yoss2fytltc/edit#gid=2045475301", sheet = "climate_risk+EAL") %>% 
  select(cbsa, normalized_inverted_climate_risk, inverted_n_eal_score)

@@

# reorder columns
col_order <-c("cbsa", "city_msa", "state", "real_estate_score", "landlord_score", "normalized_annual_renewable", "normalized_irr", "inverted_n_total_co2", "normalized_inverted_climate_risk", "inverted_n_eal_score", "inverted_n_health_emissions_cost")

@@

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(total_score_owen = cbsa, #this is just a place holder
         real_estate_score = as.numeric(real_estate_score),
         landlord_score = as.numeric(landlord_score),
         score_og_weights_EAL = cbsa
  )

@@

##### original weights with EAL score

for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$inverted_n_eal_score[i] ## EAL score
                  )
  criteria_all$score_og_weights_EAL[i] = weighted.mean(cbsa_data, criteria_weights_owen)
}

@@

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(score_climate50_prop = cbsa, #this is just a place holder
         score_climate50_prop_EAL = cbsa)

size <- dim(criteria_all)
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$normalized_inverted_climate_risk[i]
                  )
  criteria_all$score_climate50_prop[i] = weighted.mean(cbsa_data, weights_climate50_prop) 
}

### Using climate weight 50 and proportional others with EAL
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$inverted_n_eal_score[i]
                  )
  criteria_all$score_climate50_prop_EAL[i] = weighted.mean(cbsa_data, weights_climate50_prop) 
}

@@

criteria_all <- criteria_all %>% 
  rename(financial_score = normalized_irr,
         climate_impact = inverted_n_total_co2,
         health_impact = inverted_n_health_emissions_cost,
         electricity = normalized_annual_renewable,
         climate_risk = normalized_inverted_climate_risk,
         climate_EAL_risk = inverted_n_eal_score) %>% 
  mutate_if(is.numeric, ~round(., 5))

sheet_write(criteria_all, ss = "https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=0", sheet = "scores+EAL_2_2_23")
```
